### 2015-05-15 whoop.tex
Done it.

$\mutexunlock{m};$ & mutex unlock, where $m \in \mutexes$\\
\bottomrule
\end{tabular}
\caption{Forms of statements in our simple programming model}
\label{fig:statements}
\end{figure}

@@

A thread terminates if it reaches the end of $\mainforthread{T}$; in this case the thread is removed from the list of threads.  Because we are interested in the analysis of device drivers, which are \emph{reactive} concurrent programs, we do not consider the notion of global program termination.

\noindent\textbf{Lockset Instrumentation }
%
For templates $T$ and $U$ (including the possibility that $T$ and $U$ are equal) we want to check whether it is possible for a thread executing $T$ to race with a thread executing $U$, in the presence of arbitrarily many further concurrently executing threads.
%
To this end, we first \emph{instrument} a template $T$ for lockset analysis (see \S\ref{sec:background}).  Given an arbitrary symbol $i$, we define the instrumentation of $T$ with respect to $i$, denoted $\instrument{T}{i}$.  There are two aspects to this instrumentation phase: \emph{renaming} and \emph{lockset instrumentation}.

Renaming is straightforward: all occurrences of each private variable $x \in \variables{T}$ used in $T$ are replaced with a renamed variable $\instrument{x}{i}$ in $\instrument{T}{i}$, and every procedure $f \in \procedures{T}$ is renamed (both at its declaration site and at all call sites) to $\instrument{f}{i}$ in $\instrument{T}{i}$.  The purpose of renaming is to ensure that when we analyze a pair of templates, $T$ and $U$, both templates execute distinct procedures and operate on distinct private data.  This is vital in the case where $T$ and $U$ are the same.

@@

To make our analysis scalable without sacrificing precision, and to cater for recursion, we use the Houdini~\cite{flanagan2001houdini} invariant inference algorithm to automatically compute summaries (pre- and post-conditions and loop invariants) from a pool of \emph{candidate} invariants.  Given a pool of candidates, Houdini repeatedly attempts to verify each procedure with respect to its current candidate summary.  If verification fails due to an incorrect candidate, this candidate is discarded.  The process repeats until a fixpoint is reached, whereby the largest conjunction of the candidate invariants that can be proven to hold remains.  The remaining candidates, which are indeed invariants, can then be assumed during further analysis of the program.

>>>>

$\mutexunlock{m};$ & mutex unlock, where $m \in \mutexes$\\
\bottomrule
\end{tabular}
\caption{Forms of statements in our simple programming model}
\label{fig:statements}
\vspace{-2mm}
\end{figure}

@@

A thread terminates if it reaches the end of $\mainforthread{T}$, and is removed from the list of threads.  Since our interest is in analysis of device drivers, which are reactive, we do not consider the notion of global program termination.

\noindent\textbf{Lockset Instrumentation }
%
For templates $T$ and $U$ (including the possibility that $T$ and $U$ are equal) we want to check whether it is possible for a thread executing $T$ to race with a thread executing $U$, in the presence of arbitrarily many further concurrently executing threads.
%
To this end, we first \emph{instrument} a template $T$ for lockset analysis (see \S\ref{sec:background}).  Given an arbitrary symbol $i$, we define the instrumentation of $T$ with respect to $i$, denoted $\instrument{T}{i}$.  There are two aspects to this instrumentation phase: \emph{renaming} and \emph{lockset instrumentation}.
%
Renaming is straightforward: all occurrences of each private variable $x \in \variables{T}$ used in $T$ are replaced with a renamed variable $\instrument{x}{i}$ in $\instrument{T}{i}$, and every procedure $f \in \procedures{T}$ is renamed (both at its declaration site and at all call sites) to $\instrument{f}{i}$ in $\instrument{T}{i}$.  The purpose of renaming is to ensure that when we analyze a pair of templates, $T$ and $U$, both templates execute distinct procedures and operate on distinct private data.  This is vital in the case where $T$ and $U$ are the same.

@@

To make our analysis scale while maintaining precision, and to support recursion, we use the Houdini algorithm~\cite{flanagan2001houdini} to automatically compute summaries (pre- and post-conditions and loop invariants).  Given a pool of \emph{candidate} pre-conditions, post-conditions, and loop invariants, Houdini repeatedly attempts to verify each procedure.  Initially, the entire candidate pool is considered.  If verification fails due to an incorrect candidate, this candidate is discarded.  The process repeats until a fixpoint is reached.  The (possibly empty) set of remaining candidates have been proven to hold, and can used to summarize calls and loops during further program analysis.
